---
title: "Avocado Price"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(plotly)
library(tibbletime)
library(DT)
library(crosstalk)
```

<style>
.colored {
  background-color: #c6e2ff;
}
</style>

```{r include=FALSE}
# load data set
plotdata <- read.csv('avocado.csv')

# set Date as Date type variable
plotdata$Date <- as_datetime(plotdata$Date)
```

Avocado Price
======================================================================

Avocado Price {data-width=650}
-----------------------------------------------------------------------

### Average Price

```{r}
# create tibble data for avocado type
type_tibble <- plotdata %>%
        select(Date, type, AveragePrice) %>%
        arrange(Date) %>%
        group_by(type) %>%
        as_tbl_time(index = Date) %>%
        as_period('month')

# create line plot
plot_ly(data = type_tibble, 
        x = ~Date, y = ~AveragePrice, color = ~type, 
        mode = "lines+markers") %>%
        layout(title = "Average Avocado Price by Type",
               xaxis = list(title = "Year"),
               yaxis = list(title = "Average Price"))


```


Search {data-icon="fa-search"}
======================================================================

Column {data-width=250}
-----------------------------------------------------------------------

### Filters {.no-title .colored }
**Select Region**  

```{r}
# create tibble for region
region_tibble <- plotdata %>%
        select(Date, type, AveragePrice, region) %>%
        arrange(Date) %>%
        group_by(type, region) %>%
        as_tbl_time(index = Date) %>%
        as_period('month')

# Create plot data that will be used to link filters, data table, and plot.
filter_data <- SharedData$new(region_tibble)

# Create filter for region
filter_select("region", "Region", filter_data, ~region, allLevels = TRUE, multiple = FALSE)
        
```

 ***
 
 **Data table**
```{r}
# Create data table
datatable(filter_data, rownames = FALSE, 
          colnames = c('Type','Average Price', 'Region'),
          extensions = "Scroller",
          options=list(deferRender = FALSE, 
                       scrollY = 400, 
                       scrollCollapse = TRUE,
                       scroller = TRUE,
                       dom = 't'))
```
 
 
Column {data-width=750}
-----------------------------------------------------------------------
### Price by Region {.no-title .colored }

```{r}
set.seed(123)

# Create line plot
plot_ly(filter_data, x = ~Date, y = ~AveragePrice,
        color = ~type, type = 'scatter', mode = 'lines+markers') %>%
        layout(title = "Average Avocado Price by Type",
               xaxis = list(title = "Year"),
               yaxis = list(title = "Average Price"))
```


About {data-icon="fa-info-circle"}
=======================================================================

Column {data-width=600}
-----------------------------------------------------------------------

### { .colored }

**Data Source**  
The data set for this project is from [kaggle](https://www.kaggle.com/neuromusic/avocado-prices).

**Content (taken from the data set author kaggle page)**  
This data was downloaded from the Hass Avocado Board website in May of 2018 & compiled into a single CSV. Here's how the Hass Avocado Board describes the data on their website:

The table below represents weekly 2018 retail scan data for National retail volume (units) and price. Retail scan data comes directly from retailers' cash registers based on actual retail sales of Hass avocados. Starting in 2013, the table below reflects an expanded, multi-outlet retail data set. Multi-outlet reporting includes an aggregation of the following channels: grocery, mass, club, drug, dollar and military. The Average Price (of avocados) in the table reflects a per unit (per avocado) cost, even when multiple units (avocados) are sold in bags. The Product Lookup codes (PLU's) in the table are only for Hass avocados. Other varieties of avocados (e.g. greenskins) are not included in this table.

Some relevant columns in the data set:

* Date - The date of the observation
* AveragePrice - the average price of a single avocado
* type - conventional or organic
* year - the year
* Region - the city or region of the observation
* Total Volume - Total number of avocados sold
* 4046 - Total number of avocados with PLU 4046 sold
* 4225 - Total number of avocados with PLU 4225 sold
* 4770 - Total number of avocados with PLU 4770 sold

**Acknowledgements**  

Many thanks to the Hass Avocado Board for sharing this data!!

http://www.hassavocadoboard.com/retail/volume-and-price-data


Documentation {data-icon="fa-book"}
=======================================================================

Column {data-width=600}
-----------------------------------------------------------------------

### { .colored }

**About this project**  

This dashboard project utilize [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/index.html) to create interactive visualization on Avocado Data Set from [kaggle](https://www.kaggle.com/neuromusic/avocado-prices).

**Features description**  
1. Price, displays plot visualization on avocado average price from year 2015-2018 grouped by type(conventional and organic).
2. Search, by default this will display avocado average price grouped by type(conventional and organic) then region. The region can be chosen via drop down menu. The plot then will adjust its visual according to region selected


All plot displayed generated with plotly.